---
title: "Homework 5"
author: "Ying Jin"
date: "2020/11/14"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
```

## Problem 1

Read in the dataset

```{r}
url_file = 
  "https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv"

homicide_df = 
  read_csv(url(url_file)) %>% 
  mutate(
    city_state = str_c(city,state, sep = "_"),
    resolved = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest" ~ "unsolved",
      disposition == "Closed by arrest" ~ "solved",
    ) 
  ) %>% 
  select(city_state, resolved) %>% 
  filter(city_state != "Tulsa_AL")
```

Let's looke at this a bit

```{r}
aggregate_df =
homicide_df %>% 
  group_by(city_state) %>% 
  summarise(
    hom_total = n(),
    hom_unsolved = sum(resolved == "unsolved")
  )
```

Do a prop test for a single city

```{r}
prop.test(
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_unsolved),
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_total)
) %>% broom::tidy()
```

Try to iterate

```{r}
results_df = 
  aggregate_df %>% 
  mutate(
    prop_tests = map2(.x = hom_unsolved, .y = hom_total, ~prop.test(x = .x,n = .y)),
    tidy_tests = map(.x = prop_tests, ~broom::tidy(.x))
  ) %>% 
  select(-prop_tests) %>% 
  unnest(tidy_tests) %>% 
  select(city_state, estimate, conf.low, conf.high)
  
  
```

Then make a plot

```{r}
results_df %>% 
  mutate(
    city_state = fct_reorder(city_state, estimate)
  ) %>% 
  ggplot(aes(x = city_state, y = estimate)) + 
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```

##Problem 2

```{r}
exp_df = tibble(
  name = list.files("./data")
) %>% 
  mutate(
    path = str_c("./data",name, sep = "/"),
    data = map(.x = path, ~read_csv(.x))
  ) %>% 
  unnest(data) %>% 
  mutate(
   name = gsub( ".csv","", name)
  ) %>% 
  separate(name, into = c("arm","id"), sep = "_",remove = TRUE) %>% 
  select(-path) %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    names_prefix = "week_",
    values_to = "observation"
  )
```

Then make a spaghetti plot showing observations on each subject over time

```{r}
exp_df %>% 
  ggplot(aes(x = week, y = observation, color = id, group = id)) +
  geom_point(size = 1) +
  geom_line() +
  facet_grid(.~arm) +
  labs(
    title = "Observations over Eight Weeks"
  )
```

From the plot we can see that:

* Overall, the observation levels are higher in experimental arm than control arm;

* The observations at certain time in experimental arm is more disperse than control arm;

* The observation levels in experimental group increased over time while that in control groups basically stayed constant.

## Problem 3

The function to get mu_hat and p_value from t.test for a sample from N(mean ,sd = 5)

```{r}
set.seed(5)

sim_mean_p = function(samp_size = 30, mean, sigma = 5)
{
  sim_data = tibble(
    sample = rnorm(n = samp_size, mean = mean, sd = sigma)
  )
  
  sim_data %>% 
    mutate(
      p_value = t.test(sample, mu = mean) %>% broom::tidy() %>%         pull(p.value)
    ) %>% 
    summarise(
      mu_hat = mean(sample),
      p_value = mean(p_value)
    ) 
  
}

```

Set μ as 0 and iterate this function for 5000 times 

```{r}
 sim_results_zero = 
  rerun(5000, sim_mean_p(mean = 0)) %>% 
  bind_rows()
```

Repeat the above for μ={1,2,3,4,5,6}

```{r}
sim_results = 
  tibble(mu = c(1,2,3,4,5,6)) %>% 
  mutate(
    estimate_dfs = map(.x = mu, ~rerun(5000, sim_mean_p(mean = .x)))
    ) %>% 
  unnest(estimate_dfs) %>% 
  unnest(estimate_dfs)

```

add an indicator of whether  the null was rejected and count the number of times the null was rejected

```{r}
aggregate_tb = 
  sim_results %>% 
  mutate(
    conclusion = case_when(
      p_value <= 0.05 ~ "rejected",
      p_value > 0.05 ~ "fail to reject"
    )
  ) %>% 
  group_by(mu) %>% 
  summarise(
    total_n = n(),
    rejected_n = sum(conclusion == "rejected")
  )
```

